---
title: "HedgeMaster 2016 Report" 
author: 
# date: "September 26, 2016"
output: html_document
---
##*End of Year `r yy+1`*
##*`r tname`*  

  
### 1 - CORE BUSINESS: Brief Report
```{r echo=FALSE}
options(digits = 4)
my_df <- cReport_list[[i]]
knitr::kable(my_df)
      profit1 <- round(sum(my_df[, "TotalProfit"]),0)
      profit1 <- formatC(profit1, digits = 2, big.mark = ",", format="f")
```

*Total profit from running the usual business is `r profit1`*

### 2 - SCENARIO: Transactions
```{r echo=FALSE}
my_df <- sReport_list[[i]]
knitr::kable(my_df)
profit2 <- sum(my_df[,"ProT"], na.rm = T)
profit2 <- formatC(profit2, digits = 2, big.mark = ",", format="f")
```

*End of the year cash flow from Scenario-related transactions is `r profit2`*


### 3 - EXTRA EVENT: Transactions
```{r echo=FALSE}

my_df <- eReport_list[[i]]
if(nrow(my_df) == 0){
      profit3 <- 0
      profit3 <- formatC(profit3, digits = 2, big.mark = ",", format="f")
}else{
      profit3 <- sum(my_df[,"ProT"], na.rm = T)
      profit3 <- formatC(profit3, digits = 2, big.mark = ",", format="f")
      knitr::kable(my_df)
}

```

*End of the year cash flow from Extra-Event-related transactions is `r profit3`*

### 4 - EXC & OTC: Transactions 
```{r echo=FALSE}
my_df <- uReport_list[[i]]
if(nrow(my_df) == 0){
      profit4 <- 0
}else{
      profit4 <- sum(my_df[,"ProT"], na.rm = T)
      profit4 <- format(profit4,big.mark=",", trim=TRUE)
      knitr::kable(my_df)
}
profit4 <- formatC(profit4, digits = 2, big.mark = ",", format="f")

```

*End of the year cash flow from EXC & OTC transactions is `r profit4`*

### 5 - OTHER: Transactions
```{r echo=FALSE}

```
*Not Applicable.*

### 6 - Statement of Financial Position as at end of Year `r yy+1`
```{r echo=FALSE}
acc1df <- balsh_new_yy2[i,]
acc0df <- balsh_y[i,]

#asset vector[new = 1, old = 2]
ppe <- fa <- cash <- tasset <- sharecap <- re <- tasset <- tequity <- loan <- tEL <- vector()
ppe[1] <- acc1df[1,2]; ppe[2] <- acc0df[1,2]; ppeN <- formatC(ppe, digits = 2, big.mark = ",", format="f")
fa[1] <- acc1df[1,3]; fa[2] <- acc0df[1,3]; faN <-formatC(fa, digits = 2, big.mark = ",", format="f")
cash[1] <- acc1df[1,4]; cash[2] <- acc0df[1,4]; cashN <- formatC(cash, digits = 2, big.mark = ",", format="f")
for(i in 1:2){
      tasset[i] <- sum(as.numeric(c(ppe[i],fa[i],cash[i])))
}; tassetN <- formatC(tasset, digits = 2, big.mark = ",", format="f")

#equity
sharecap[1] <- acc1df[1,5]; sharecap[2] <- acc0df[1,5]; sharecapN <- formatC(sharecap, digits = 2, big.mark = ",", format="f")
re[1] <- acc1df[1,6]; re[2] <- acc0df[1,6]; reN <- formatC(re, digits = 2, big.mark = ",", format="f")

for(i in 1:2){
      tequity[i] <- sum(as.numeric(c(sharecap[i],re[i])))
}; tequityN <- formatC(tequity, digits = 2, big.mark = ",", format="f")

loan[1] <- acc1df[1,7]; loan[2] <- acc0df[1,7]; loanN <- formatC(loan, digits = 2, big.mark = ",", format="f")
      #tequity+loan
for(i in 1:2){
      tEL[i] = sum(as.numeric(c(loan[i], tequity[i])))
}; tELN <- formatC(tEL, digits = 2, big.mark = ",", format="f")

tname2 <- toupper(tname)
```

####**`r tname2`**  
####**STATEMENT OF FINANCIAL POSITION**  
####**AS AT END OF YEAR `r yy+1`**  

|             | AS AT END OF YR `r yy+1` |  AS AT END OF YR `r yy` |
|---------------------:|:---------------|----------------|
|             | (RM)  | (RM)    |
| **ASSETS**  |       |         |
| PPE                         | `r ppeN[1]`        | `r ppeN[2]`        | 
| Financial Asset             | `r faN[1]`         | `r faN[2]`         |
| Cash                        | `r cashN[1]`       | `r cashN[2]`       | 
| **Total Assets**            | `r tassetN[1]`     | `r tassetN[2]`     |
|  |  |  | 
| **EQUITY AND LIABILITIES** |  |  |
| **Equity attributable to owners of the company** |  |  | 
| Share Capital               | `r sharecapN[1]`   | `r sharecapN[2]`   | 
| Retained Earnings           | `r reN[1]`         | `r reN[2]`         |
| **Total equity**            | `r tequityN[1]`    | `r tequityN[2]`    | 
|  |  |  | 
| **Liabilities** |  |  | 
| Loan                  | `r loanN[1]` | `r loanN[2]` |
| **Total liabilities** | `r loanN[1]` | `r loanN[2]` | 
|  |  |  | 
| **Total equity and liabilities**        | `r tELN[1]` | `r tELN[2]` | 
|  |  |  | 
| *Net assets attributable to owners (NAV)* | `r tequityN[1]` | `r tequityN[2]` | 


###7 - EVALUATION ~ Hedging `r tname`
```{r, echo=FALSE, fig.show='hold', fig.height=17, fig.width=22.5}

my_df <- scoredf_byteam_list[[i]]; scorehedging <- my_df[1,yy+2]

A02.f.dir <- "C:/Users/User/Google Drive/z_ALLHM"
setwd(A02.f.dir); source("A02_Reportf.R")

prosimTdf_list <- prolist.f(fdf8_td, tname, yy)              
               
#cru1, pal2, eur3, golusd4
#loop for cru, pal and gol
class1 <- c("CRU","PAL", "EUR", "GOL", "USD"); class2 <- c("CRU","PAL", "EUR", "USD", "GOL")

plotUlist <- lapply(c(1,2,4), FUN = function(q){
{
dfa <- prosimTdf_list[[q]]; ss0 <- dfa[31, "xU"] 
#"NoHedge.C", "User.C", "Aggregate.C", "NoHedge.U", "User.U", "Aggregate.U", "xU", "xC"
m.var <- c("NoHedge.U", "User.U", "Aggregate.U")
replace.m <- c("Without Hedge", "Your Transactions", "Aggregate Portfolio")
                                                                 
dfb <- melt(dfa, id.vars = "xU", measure.vars = m.var)
levels(dfb$variable) <- replace.m

xlab <- paste0("Spot price of ", class1[q] , " at time T, ST")
colnames(dfb) <- c("x", "Portfolio", "value");
}
      
if(min(dfb[,"value"]) ==0 & max(dfb[,"value"]) ==0){
      ddg <- 0
}else{ddg <- 0.1}
p1 <- ggplot(dfb, aes(x=x, y=value, colour=Portfolio)) +
      # geom_line(alpha=0.9, size = 1, position= position_dodge(ddg)) + 
      # geom_line(alpha=0.8, size = 1.2, position=position_jitter(width=ddg, height=ddg)) + 
      geom_line(alpha=1, size = 1.2)+
      xlab(label = xlab) +
      ylab(label = "Cash flow at time T") +
      ggtitle("Simulated cash flow of various portfolio based on varying spot prices")+
      geom_hline(aes(yintercept=0), colour="grey", linetype="solid", size = 0.6) +       
      geom_vline(aes(xintercept=ss0), colour="black", linetype="dashed", size = 1.25) + 
      geom_text(aes(x = ss0, y = 0, label = paste0("S0 = ",ss0)), size = 3.5, hjust = -0.1, vjust = 2) 

p1


      
})

plotClist <- lapply(c(3,4), FUN = function(q){
{
      
dfa <- prosimTdf_list[[q]]; ss0 <- dfa[31, "xC"] 
#"NoHedge.C", "User.C", "Aggregate.C", "NoHedge.U", "User.U", "Aggregate.U", "xU", "xC"
m.var <- c("NoHedge.C", "User.C", "Aggregate.C")
replace.m <- c("Without Hedge", "Your Transactions", "Aggregate Portfolio")
                                                                 
dfb <- melt(dfa, id.vars = "xC", measure.vars = m.var)
levels(dfb$variable) <- replace.m

xlab <- paste0("Spot price of ", class2[q] , " at time T, ST")
colnames(dfb) <- c("x", "Portfolio", "value")
}
      
if(min(dfb[,"value"]) ==0 & max(dfb[,"value"]) ==0){
      ddg <- 0
}else{ddg <- 0.1}
p1 <- ggplot(dfb, aes(x=x, y=value, color=Portfolio)) +
      # geom_line(alpha=0.9, size = 1) +
      # geom_line(alpha=0.9, size = 1.2, position= position_dodge(ddg)) + 
      # geom_line(alpha=0.8, size = 1.2, position=position_jitter(width=ddg, height=ddg)) +
      geom_line(alpha=1, size = 1.2)+
      xlab(label = xlab) +
      ylab(label = "Cash flow at time T") +
      # ylim(miny, maxy) + 
      ggtitle("Simulated cash flow of various portfolio based on varying spot prices")+
      geom_hline(aes(yintercept=0), colour="black", linetype="solid", size = 0.6) +       
      geom_vline(aes(xintercept=ss0), colour="black", linetype="dashed", size = 1.25) + 
      geom_text(aes(x = ss0, y = 0, label = paste0("S0 = ",ss0)), size = 3.5, hjust = -0.1, vjust = 2) 

p1

})
      


# plot 5 graphs
plot_grid(plotUlist[[1]], plotUlist[[2]], plotUlist[[3]], plotClist[[1]], plotClist[[2]], align='h', ncol = 2)



```

*The score for this section (Hedging) is `r scorehedging`*

###8 - EVALUATION ~ Cash Flow
```{r echo=FALSE}
my_df <- scoredf_byteam_list[[i]]
c.score <- my_df[2,yy+2]
if(c.score == 0){
      msg <- "Your company's cash balance falls below 0. A short term loan with an interest of 12% is borrowed automatically from a 3rd party bank. The loan will be repaid fully by the end of next year. The loan amount taken up is the amount required to reach a cash balance of MYR 1 million. E.g. If your cash balance is -2 million after the trading period, a loan of 3 million will be taken, so that the post-cash balance is 1 million."
     
}else{
      msg <- "Your company's cash balance remains positive."
}
```

*`r msg`*  

*The score for this Cash Flow Evaluation section is `r c.score`.*

###9 - EVALUATION ~ Extra Event
```{r echo=FALSE}
if(yy %in% c(0,1)){
      df <- fdf8_td
      u1 <- df[, "TeamName"] == tname; u2 <- df[, "cType"] == "Employ Service";
      u3 <- df[,"tDate"] == yy
      if(sum(u1 & u2 & u3) > 0){
            servchosen <- df[u1 & u2 & u3, "FIC"]
      }else{servchosen <- "None"}
      
            e.score <- scoredf_byteam_list[[i]][3,yy+2]
msg <- paste0(servchosen, " was chosen. The score for Extra Event this year is ", e.score)
      
}else if(yy == 4){
       u1 <- df[, "TeamName"] == tname; u2 <- df[, "cParty"] == "Harry M."
       u3 <- df[,"tDate"] == yy
       if(sum(u1 & u2 & u3) > 0){
            ursharpe <- df[u1 & u2 & u3, "kPrice"]
       }else{
            ursharpe <- "NA"
       }

msg <- paste0("The sharpe ratio computed from the input weightage is ,", ursharpe, ". The maximum sharpe ratio is ", maxsharpeR1, ". The score is ", e.score, " .")
       
}else{
      "Not Applicable"
}
```

*`r msg`*


###10 - Total Score Breakdown - `r tname`
```{r echo=FALSE}
my_df <- scoredf_byteam_list[[i]]
knitr::kable(my_df)

h.score <- my_df[1,yy+2]
c.score <- my_df[2,yy+2]
e.score <- my_df[3,yy+2]
n.score <- my_df[4,yy+2]
if(n.score == 0){
      msg <- paste0("*Score(NAV) will be measured at the end of Year 5. Score(NAV) will be 0 for other years.")
}
```

*`r msg`*