---
title: "Extra Event"
author: "HedgeMaster Challenge 2016"
date: "November 13, 2016"
output: pdf_document
---

```{r, echo = FALSE}
library(knitr)
yr <- paydate <- 1
sector <- "Alpha"
eventname <- "ProService AA"; eventname.full <- paste0(eventname, " (", sector, ")")
servicename.v <- c("Service AA1", "Service AA2", "Service AA3")
upfrontcost.v <- c("RM 1,800,000.00", "RM 1,800,000.00", "RM 1,500,000.00")
      EndofYear <- 2:5
            CostReductionPerUnit1 <- c(500,510,520,530)
            CostReductionPerUnit2 <- c(40,42,44,46)      
            CostReductionPerUnit3 <- c(180,185,190,195)
            
elink <- "https://1drv.ms/xs/s!AuUxik9_I7qcjj0Q_9R9L54asCuW"      
            
if(sector %in% "Alpha"){
      note1 <- "Each year, Alpha company will produce 1500 units of GOL, 20000 units of CRU, 3000 units of PAL."
}else{
      note1 <- "Each year, Beta company will produce 1500 units of GOL2, 20000 units of CRU2, 3000 units of PAL2."
}

servA1.df <- data.frame(EndofYear, CostReductionPerUnit = CostReductionPerUnit1 )
servA2.df <- data.frame(EndofYear, CostReductionPerUnit = CostReductionPerUnit2 )
servA3.df <- data.frame(EndofYear, CostReductionPerUnit = CostReductionPerUnit3 )

```

#`r eventname.full`
##End of Year `r yr` 

You have just received a contract offer by ProTech Bhd. The contract offers professional services that would enhance your firm's productivity in terms of lower cost per unit. The following are the list of services:


(@) **`r servicename.v[1]`**:
Professional services that would lower your firm's production cost of GOLD (GOL). The cost reductions per unit (in RM) are as follow:

```{r, echo=FALSE}
kable(servA1.df,format.args = list(big.marks = ","))
```

The total upfront cost for this service is `r upfrontcost.v[1]` and is payable at the End of Year `r paydate`.

(@) **`r servicename.v[2]`**:
Professional services that would lower your firm's production cost of Crude Oil (CRU). The cost reductions per unit (in RM) are as follow:

```{r, echo=FALSE}
kable(servA2.df,format.args = list(big.marks = ","))
```

The total upfront cost for this service is `r upfrontcost.v[2]` and is payable at the End of Year `r paydate`.

(@) **`r servicename.v[3]`**: 
Professional services that would lower your firm's production cost of Palm Oil (PAL). The cost reductions per unit (in RM) are as follow:

```{r, echo=FALSE}
kable(servA3.df,format.args = list(big.marks = ","))
```

The total upfront cost for this service is `r upfrontcost.v[3]` and is payable at the End of Year `r paydate`.

###Note: 
`r note1`

###Link:
Go to this link and select your choice of service.  
click: __<`r elink`>__

####Note 2:
If there are more than one submission from the same team, the latest submission will be considered instead.

