---
title: "HedgeMaster Challenge 2016"
author: "Sunway Actuarial & Financial Excellence (SAFE)"
date: "November 13, 2016"
output: pdf_document
---

##*`r TeamName.c`*  
##*End of Year `r yy+1` Report*
  
### 1 - CORE BUSINESS: Brief Report
```{r echo=FALSE}
knitr::kable(c1Report.df, row.names = F)
```

`r cExtra.msg.c`  
  
`r cComment.c`  

### 2 - Relevant Transactions
```{r echo=FALSE, fig.width = 10}
knitr::kable(r2Report.df[order(r2Report.df[,"TransactionClass"]),1:6], row.names = F)
knitr::kable(r2Report.df[order(r2Report.df[,"TransactionClass"]),c(1, 7:12)], row.names = F)
knitr::kable(r2Report.df[order(r2Report.df[,"TransactionClass"]),c(1, 13:16)], row.names = F)
```

`r r2Comment0.c`  

`r r2CommentT.c`

### 3 - Failed Transactions
```{r echo=FALSE, results='asis'}
if(nrow(f2Report.df)>0){
       return(knitr::kable(f2Report.df[,1:6], row.names = F))
}  
if(nrow(f2Report.df)>0){
      return(knitr::kable(f2Report.df[,c(1, 7:12)], row.names = F))
}
if(nrow(f2Report.df)>0){
      return(knitr::kable(f2Report.df[,c(1, 13:17)], row.names = F))
}
```

`r f2Comment.c`

### 4 - Statement of Financial Position  

`r TeamName.c`  

STATEMENT OF FINANCIAL POSITION  

AS AT END OF YEAR `r yy+1`  


|                      | AS AT END OF YR `r yy+1`  |  AS AT END OF YR `r yy` |
|---------------------:|:--------------------------|-------------------------|
|                      | (RM)                         | (RM)                  |
| **ASSETS**           |                              |                       |
| PPE                         | `r accelementy2.v[1]`  | `r accelementy.v[1]` | 
| Financial Asset             | `r accelementy2.v[2]`  | `r accelementy.v[2]` |
| Cash                        | `r accelementy2.v[3]`  | `r accelementy.v[3]` |
| **Total Assets**            | `r accelementy2.v[4]`  | `r accelementy.v[4]` |
|  |  |  | 
| **EQUITY AND LIABILITIES** |  |  |
| **Equity attributable to owners of the company**  |  |  | 
| Share Capital               | `r accelementy2.v[5]`  | `r accelementy.v[5]` | 
| Retained Earnings           | `r accelementy2.v[6]`  | `r accelementy.v[6]` |
| **Total equity**            | `r accelementy2.v[7]`  | `r accelementy.v[7]` | 
|  |  |  | 
| **Liabilities** |  |        | 
| Loan                        | `r accelementy2.v[8]`  | `r accelementy.v[8]` |
| **Total liabilities**       | `r accelementy2.v[9]`  | `r accelementy.v[9]` | 
|  |  |  | 
| **Total equity and liabilities**                    | `r accelementy2.v[10]` | `r accelementy.v[10]` | 
|  |  |  | 
| *Net assets attributable to owners (NAV)*           | `r accelementy2.v[11]` | `r accelementy.v[11]` | 



###5 - EVALUATION ~ Hedging
```{r echo=FALSE, fig.width=7, fig.height=4}
# plot_grid(ggplot.asset.list[[1]],ggplot.asset.list[[2]], ggplot.asset.list[[3]],ggplot.asset.list[[4]],
#           ggplot.asset.list[[5]], align='h', ncol = 1)
ggplot.asset.list[[1]]
ggplot.asset.list[[2]]
ggplot.asset.list[[3]]
ggplot.asset.list[[4]]
ggplot.asset.list[[5]]

knitr::kable(hedgescore.team.df, row.names = F)

adddetails.link <- "https://1drv.ms/b/s!AuUxik9_I7qcngRnq49ffpmZhpa_"

```
  
`r hedge5Comment.c`   

   
*It is possible that the Hedging Score exceed 20 points. Anyhow, your score will be compared relatively to other teams.    
Additional details on Hedging Score and Payoff Graph can be found here:    
click: **<`r adddetails.link`>**

###6 - EVALUATION ~ Cash Flow  
`r cash6Comment.c`

###7 - EVALUATION ~ Extra Event
`r extra7Comment.c` 
   
###8 - Total Score Breakdown - `r TeamName.c`  
```{r echo=FALSE}
knitr::kable(scorebr8.yy2.df, row.names = F)
```
   
`r scoreComment8.c`
 